---
title: "Secrets Behind the Boost of Companies"
subtitle: "States, industry, number of years company founded and the continuous growth are the main factors that contributes to the Boost."
author: 
  - Zhiyue Yu
thanks: "Code and data are available at: https://github.com/gggeorgeeeyu/304final."
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "Businesses and companies are one of the main roles that maintain the daily operation of our society. The purpose of a company is to solve a social problem and improve people's life, it is true both for large companies and for startups. The better the product or service a company provides, the faster it grows. Our mostly-cleaned data is obtained from the data world, which contains the data set that describes entrepreneurship and company activities. The original data is from Inc.com, which ranks the top 5000 fast growing companies in the US. We find that there are a number of factors that may influence the growth of a company, such as the States they are in, the industry they are in, the number of years the companies has been founded and the continuous growth, or the long-term performance may effect the boost in 2019. Our finding provides insights and principles for companies for further growth, including but not just limit to year 2019."
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(readr)
library(tidyverse)
library(dplyr)
```

# Introduction

Businesses and companies are one of the main roles that maintain the daily operation of our society. Regardlesss the history and industry of the companies, the purpose of a company is to solve a social problem and improve people's life, it is true both for large companies and for startups. The better the product or service a company provides, the faster it grows. 

In Section \@ref(data), we cleaned the data, fitted a multi-linear regression model with the data and analyzed the result. Our mostly-cleaned data is obtained from the data world(@citea), which contains the data set that describes entrepreneurship and company activities. The original data is from Inc.com(@citeb), which ranks the top 5000 fast growing companies in the US. All the other related company information can be found in the hidden links by clicking at the comapny names.

We find that there are a number of factors that may influence the growth of a company, such as the States they are in, the industry they are in, the number of years the companies has been founded and the continuous growth, or the long-term performance may effect the boost in 2019. For each aspect, we conducted a comprehensive analysis in Section \@ref(discussion). Our finding provides insights and principles for companies for further growth, including but not just limited to year 2019. We believe that the specific reason for a successful company may vary, but the logic and rules behind it is constant.





You can and should cross-reference sections and sub-sections. For instance, Section \@ref(data). R Markdown automatically makes the sections lower case and adds a dash to spaces to generate labels, for instance, Section \@ref(first-discussion-point). 



# Data

```{r, include=FALSE}
raw_data <- read.csv("https://query.data.world/s/ni2vh2lfsi4qm3ytuiijjn7fpgkxyc", header=TRUE, stringsAsFactors=FALSE)
```

```{r, include=FALSE}
#change the variable names
names(raw_data)[6] <- "revenue"
names(raw_data)[7] <- "growth_in_percentage"
names(raw_data)[8] <- "industry"
names(raw_data)[9] <- "num_of_workers"
names(raw_data)[10] <- "year_founded"
names(raw_data)[11] <- "num_of_years_onlist"
names(raw_data)[12] <- "pre_num_of_workers"
raw_data$year_founded[is.na(raw_data$year_founded)] <- 2010

#choose the columns we need
#data1 is for graphing 
data1 <- raw_data %>%
  select(name, state, revenue, growth_in_percentage, industry, num_of_workers, year_founded, num_of_years_onlist, pre_num_of_workers)

#data2 is for fitting model
data2 = data1

data2[data2 == "Advertising & Marketing"] <- 1
data2[data2 == "Logistics & Transportation"] <- 2
data2[data2 == "Food & Beverage"] <- 3
data2[data2 == "Consumer Products & Services"] <- 4
data2[data2 == "Retail"] <- 5
data2[data2 == "Health"] <- 6
data2[data2 == "Telecommunications"] <- 7
data2[data2 == "Financial Services"] <- 8
data2[data2 == "Computer Hardware"] <- 9
data2[data2 == "Software"] <- 10
data2[data2 == "Energy"] <- 11
data2[data2 == "Government Services"] <- 12
data2[data2 == "Real Estate"] <- 13
data2[data2 == "Manufacturing"] <- 14
data2[data2 == "Media"] <- 15
data2[data2 == "Construction"] <- 16
data2[data2 == "IT System Development"] <- 17
data2[data2 == "Travel & Hospitality"] <- 18
data2[data2 == "Security"] <- 19
data2[data2 == "IT Management"] <- 20
data2[data2 == "Human Resources"] <- 21
data2[data2 == "Environmental Services"] <- 22
data2[data2 == "Insurance"] <- 23
data2[data2 == "Business Products & Services"] <- 24
data2[data2 == "Education"] <- 25
data2[data2 == "Engineering"] <- 26
data2[data2 == "IT Services"] <- 27
```


```{r， include = FALSE}
model <- lm(growth_in_percentage ~ state + industry + num_of_workers + year_founded + num_of_years_onlist + pre_num_of_workers , data = data2)
summary(model)
```

Variable names                        | Estimate    | Std. Error.   | z value      | Pr>\|z\|
------------------------------------- |------------ |-------------- |------------- |-------------
(Intercept)                           |-2.788e+03   |1.207e+03      |-2.310        |0.02091  *  
stateID                               |8.221e+02    |3.191e+02      |2.576         |0.01003  * 
stateNM                               |2.791e+03    |5.029e+02      |5.549         |3.02e-08 ***
Construction                          |-1.786e+02   |8.947e+01      |-1.996        |0.04601  *
Logistics & Transportation            |2.382e+02    |0.20041        |-3.189        |0.001429 ** 
Business Products & Services          |-1.657e+02   |8.123e+01      |-2.040        |0.04137  ***
IT Services                           |-4.506e+02   |2.014e+02      |2.237         |0.02532  *
year_founded                          |1.748e+00    |5.936e-01      |2.944         |0.00325  **
num_of_years_onlist                   |-8.826e+01   |8.059e+00      |-10.952       |< 2e-16  ***






Our data is of penguins (Figure \@ref(fig:bills)).

```{r bills, fig.cap="Bills of penguins", echo = FALSE}

```

# Model

\begin{equation}
Pr(\theta | y) = \frac{Pr(y | \theta) Pr(\theta)}{Pr(y)}  (\#eq:bayes)
\end{equation}

Equation \@ref(eq:bayes) seems useful, eh?

Here's a dumb example of how to use some references: In paper we run our analysis in `R` [@citeR]. We also use the `tidyverse` which was written by @thereferencecanbewhatever If we were interested in baseball data then @citeLahman could be useful. 

We can use maths by including latex between dollar signs, for instance $\theta$.


# Results

# Discussion

## First discussion point

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this. 

## Second discussion point

## Third discussion point

## Weaknesses and next steps



\newpage

\appendix

# Appendix {-}


# Additional details


\newpage


# References


b. https://www.inc.com/inc5000/2019

a. https://data.world/ashok/entrepreneurship-data/workspace/project-summary?agentid=ashok&datasetid=entrepreneurship-data

